MaxEnt: What is it good for?

### 2015-06-18 ms.tex
Abstract and intro words

\documentclass[letterpaper, 11pt]{article}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage[left=2.5cm,top=2.5cm,right=2.5cm]{geometry}
\usepackage{parskip}
\usepackage{amsmath}
\usepackage{dsfont}
\usepackage[utf8]{inputenc}

@@

The principle of maximum entropy (MaxEnt) is an idea in probability theory
that is usually associated with \citet{jaynes}. The principle may be used
to {\it assign} or {\it update} a
subjective\footnote{in the sense that the probability distribution is a model
of the state of uncertainty of an idealised rational agent, rather than
a {\it frequency distribution} such as a histogram of people's heights.}
probability distribution when you obtain a certain kind of information
called {\it testable information}. The principle is very intuitively compelling
and there are some axiomatic arguments in its favour
\citep[e.g.][]{2010arXiv1008.4831K}. However, MaxEnt has also been widely
misapplied (even by some of its staunchest defenders), misunderstood,
and poorly defended (at times, even by Jaynes himself).
Consequently, most modern Bayesians pay little attention to the principle,
although there is a tendency among physicists to invoke it as a justification
for a prior distribution (be it uniform, exponential, gaussian, or whatever).
The purpose of this article is to explore the principle from the point of
view of a Bayesian practitioner, discuss some of the properties that
make MaxEnt compelling, and propose some ideas about how it could be used in
practice.

>>>>

\documentclass[a4paper, 11pt]{article}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage[left=2.5cm,top=2.5cm,right=2.5cm]{geometry}
\usepackage{parskip}
\usepackage{amsmath}
\usepackage{dsfont}
\usepackage[utf8]{inputenc}

@@

\abstract{I discuss the principle of maximum (relative) entropy as a tool
for updating probability distributions. This principle is intuitively
compelling, as I will show through examples. However, it has been neglected
by most modern practitioners of Bayesian inference. I will argue that there
are two main reasons for this: i) some questionable applications
and discussions of the principle have appeared in the literature, and
ii) the situation which the principle seems designed to handle never seems
to arise in practical applications.}

\section{Introduction}
The principle of maximum entropy (MaxEnt) is an idea in probability theory
that is usually associated with \citet{jaynes}, although it has appeared in
various guises in the work of others \citep[e.g.][]{gibbs, boltzmann, shannon}.

The principle may be used
to {\it assign} or {\it update} a
subjective\footnote{in the sense that the probability distribution is a model
of the state of uncertainty of an idealised rational agent, rather than
a {\it frequency distribution} such as a histogram of people's heights.}
probability distribution when you obtain a certain kind of information
called {\it testable information}. In this article I will focus on the
updating application, as the assigning application can be viewed as a special
case where the prior distribution happened to be
uniform\footnote{A uniform probability distribution, either over a discrete
hypothesis space, or a continuous one with respect to a continuous, may be
justified by a symmetry argument or simply asserted as in the
``subjective Bayesian'' approach.}.

The principle is very intuitively compelling
and there are some axiomatic arguments in its favour
\citep[e.g.][]{2010arXiv1008.4831K}. However, MaxEnt has also been widely
misapplied (even by some of its staunchest defenders), misunderstood,
and poorly defended (at times, even by Jaynes himself).
Consequently, most modern Bayesians pay little attention to the principle,
although there is a tendency among physicists to invoke it as a justification
for a prior distribution (be it uniform, exponential, gaussian, or whatever).
The purpose of this article is to explore the principle from the point of
view of a Bayesian practitioner, discuss some of the properties that
make MaxEnt compelling, and propose some ideas about how it could be used in
practice.
